\section{Describing the company:}
 Internship is carried out in a startup company named Vion Labs. Vion labs is a digital media technology startup which focuses in providing a state of the art, innovative and appealing product for movie enthusiasts in the form of movie recommendation engine. A recent study by eMarketer in USA expects that an US adults to spend around 5 hours 46 minutes of their time per day in getting involved in digital media \cite{Mobil1:online}. As per movie on demand provider NetFlix, it has been observed that a average subscriber spends approximately 1 hour and 44 minutes streaming the video content \cite{HowM2:online}. From these studies it is clear that an average person spends most of his leisure time involving activities like watching movies, television and playing games in the digital world. Hence our startup Vion labs has been focusing in digital media market to target a large number of customers in this segment. \\
 
 The method used for describing product or a service provided by a company is based on these following areas:
 
 \begin{itemize}
 
  \item Features : 
  The stand out and most attractive features that company can offer in the product. The latest product of Vion labs is named as  "Vionel", which is a website with a personalized movie recommendation platform. It has an appealing user friendly front end containing information about latest movies. It also has information about content providers, from where the users can get access to the video content. One of the attractive feature of Vionel is that it provides a social media type of platform to share personal views, likes and dislikes about a movie in the form of comments. \\
  The recommendation engine assigns a rating percentage score based on the popularity of a movie, which helps the user to chose movies with highest ratings. The front end of the website provides the user with the option to list movies based on different genres, keywords and characters involved in the movies. The feature of searching movies based on the tags for eg. "adventure, action,comedy etc" is also a part of Vionel's frontend. \\
  Vionel provides its users with a lot of different dimensions of critically analyzing a movies. Future features to be included in the vionel website include relationship graphs among characters in the movies. Advertisement free website is one of the stand out feature of Vionel product, which creates a non-intrusive environment for the users to browse through movies. On the other hand Vionel provides an excellent platform for the partner companies and other movie franchises to advertise their movies in Vionel website.      
      
  \item Advantages : The sustainable competitive advantage of the company's product compared to its competitors. Vionel is able to excel in the domain of providing accurate recommendations for movies unlike its competitors. The accuracy of the movies recommended for the selection of the user is currently not optimal by the recommendation engine of Netflix and other movie on demand service. Whereas the recommendation engine of Vionel is able to recommend users with an appropriate list of movies based on one's choice. The main advantage of Vionel is that it provides an user friendly social media platform for discussing and sharing one's view about the movies and the characters in the movies. \\
  The list of related movies for a movie provided by Vionel's recommendation engine is very closely related. The feature of bookmarking one's choice of movies and storing it in one's profile is a new feature in internet movie database websites and Vionel has this feature. Vionel provides the movie franchise owners to advertise their movies and trailer videos related to the movie. Vionel also provides the movie creators with the social advertisement platform to collect opinions about movies from the viewers.      	   
   
  \item Returns for the customer : The current problems of the customer that is solved by the service or product. Vionel provides its customers with a free website to enrich their movie selection experience. It provides with a personalized movie recommendation website with personal bookmarks of movies and also pointers to where the users can access the movie content. It also provides a user friendly social environment to discuss one's views about the movies. The website provides a one stop solution for all the movie enthusiasts to ponder upon latest content in the entertainment world and stumble upon the movie to watch in lesser time than searching in internet. Vionel provides the movie creators and its advertisement agencies to showcase trailers or teasers of the movies and also to collect valuable opinions and general public comments about the movies. Finally, the new and innovative features that are planned to be a part of Vionel product are from the internship work of automatic brand logo detection in movies to generate tag or category of movies namely "Movies with product placement". Further this tag is used to provide better suggestions for the users of Vionel. Thereby assisting the movie recommendation engine to showcase the list of best possible movies based on user's choice and search behavior.\\      
 \end{itemize}
 
 Framework of innovation process of a new product or service provided by startup consists of three stages, namely conceptualization of the new product, development of working prototype of the product and the last phase is regarding commercializing the developed product. Vionel product is in the beginning of commercialization phase of frame innovation process.
 
 \section{Research question}
 Currently Vionel as a product is in the market launch phase and hence there is a need for market research in order to attract users in large amount to visit our website. Since our product is a website, process of marketing and creation of brand awareness is highly benefited by online marketing strategy. Even though there exists a number of other marketing strategies such as word of mouth, direct marketing and others. In the area of online marketing, impact and use of social media is pivotal. The use of social media for this purpose enables the marketing team to reach out to a larger audience in an time efficient and effective manner.\\
 Hence the research question that will be answered in the following minor thesis would be to understand the      
       
 
  
                        